US General Society Survey Analysis

### 2024-03-14 paper/paper.qmd
Made a linear model

library(tidyverse)
library(patchwork)
```

@@

#plot 2016 votes against employment status and gender
#SO MANY NA VALUES???
ces2020_votes %>%
  ggplot(aes(x= employ, fill=presvote16post)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  coord_flip() +
  labs(x ="Employment status",
      y = "Count of votes",
      fill = "Vote in 2016")

@@

@@

# Appendix {-}

>>>>

library(tidyverse)
library(patchwork)
library(gridExtra)
```

@@

#plot 2016 votes against employment status and gender
#SO MANY NA VALUES???
ces2020_votes %>%
  ggplot(aes(x= employ, fill=presvote16post)) +
  stat_count(position = "dodge") +
  facet_wrap(facets = vars(gender)) +
  theme_minimal() +
  coord_flip() +
  labs(x ="Employment status",
      y = "Count of votes",
      fill = "Vote in 2016")
```

```{r, fig.height=4, fig.width=8}
```

@@

```{r}
# Calculate percentages
percentage_data <- ces2020_votes %>%
  group_by(birthyr) %>%
  summarise(HillaryClinton = sum(presvote16post == "Hillary Clinton") / n() * 100,
            DonaldTrump = sum(presvote16post == "Donald Trump") / n() * 100,
            Other = sum(presvote16post == "Other") / n() * 100,
            DidNotVote = sum(presvote16post == "Did not Vote") / n() * 100) %>%
  ungroup()

# Reshape data to long format
percentage_data_long <- pivot_longer(percentage_data, cols = -birthyr, names_to = "Candidate", values_to = "Percentage")

plot_hillary <- ggplot(percentage_data_long %>% filter(Candidate == "HillaryClinton"), aes(x = birthyr, y = Percentage)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(title = "Percentage for Hillary Clinton", y = "Percentage (%)") +
  theme_minimal()
plot_hillary

plot_trump <- ggplot(percentage_data_long %>% filter(Candidate == "DonaldTrump"), aes(x = birthyr, y = Percentage)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(title = "Percentage for Donald Trump", y = "Percentage (%)") +
  theme_minimal()
plot_trump

plot_other <- ggplot(percentage_data_long %>% filter(Candidate == "Other"), aes(x = birthyr, y = Percentage)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(title = "Percentage for Other", y = "Percentage (%)") +
  theme_minimal()
plot_other

@@

# Appendix {.unnumbered}
